NGO analysis

### 2022-07-21 Shiny/Test/Flexdashboard rows.Rmd
Fixing public grants value box reference.

### KPI
```{r}
valueBoxOutput("KPI_box_admin")
```

@@

### KPI 5
```{r}
valueBoxOutput("KPI_box5")
```

@@

  output$KPI_box5 <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_public_num()),
      caption = "Public grants growth",
      color = ifelse(KPI_public_num() < 100, "warning", "success"),
      icon = "fas fa-hand-holding-usd"
    )
  })

>>>>

### KPI 1
```{r}
valueBoxOutput("KPI_box_admin")
```

@@

### KPI 5
```{r}
valueBoxOutput("KPI_box_public")
```

@@

  output$KPI_box_public <- renderValueBox({
    valueBox(
      value = KPI_to_string(KPI_public_num()),
      caption = "Public grants growth",
      color = ifelse(KPI_public_num() < 100, "warning", "success"),
      icon = "fas fa-hand-holding-usd"
    )
  })
